---
title: "Penguins ANOVA"
author: "Sara Orofino"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#{.tabset}

##Step 1.
1. Load packages and read-in penguins.csv data

```{r, include=FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our question:  
  
Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, Adelie)?  

##Step 2. 

2. Do some exploring  

New functions: with + table for easy counting over multiple facotrs  

Update species name using case_when  

```{r}

counts <- with(penguins, table(species, sex)) # with tells r to create something with something else, table counts number of penguins by species column and sex  

penguins2 <- penguins %>% 
  mutate(common_name = 
          case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "adelie"
        )
        ) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")


```

- Exploratory graphs  
- Summary statistics  
- Levene's tests for equal variances  
- one way ANOVA  
- post-hoc testing  

```{r}

hists <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~common_name)

hists

qq <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq() +
  facet_wrap(~ common_name)

qq

# Levene's test for equal variance (>2 groups... if you have two groups, use the F-test for equal variance)

# We'll use the function leveneTest from the 'car' package

#H0: Variances are equal
#HA: Variances are unequal

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)
penguin_levene

# We retain the null hypothesis of equal variances (p = 0.06)

# If the highest is less than 4x greater your smallest variance can use an ANOVA. Make a real quick summary table to compare the differences in variances of flipper length by common name. 

variances <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    variance = var(flipper_length)
  )
variances
```



