---
title: "Penguins ANOVA"
author: "Sara Orofino"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#{.tabset}

##Step 1.
1. Load packages and read-in penguins.csv data

```{r, include=FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our question:  
  
Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, Adelie)?  

##Step 2. 

2. Do some exploring  

New functions: with + table for easy counting over multiple facotrs  

Update species name using case_when  

```{r}

counts <- with(penguins, table(species, sex)) # with tells r to create something with something else, table counts number of penguins by species column and sex  

penguins2 <- penguins %>% 
  mutate(common_name = 
          case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "adelie"
        )
        ) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")


```

- Exploratory graphs
- Summary statistics
- Levene's tests for equal variances
- one way ANOVA
- post-hoc testing




